Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-17 paper/manuscript.tex
Rearrange and resize RMSD_heatmap figure

\begin{SCfigure*}[\sidecaptionrelwidth][t]
\centering
\includegraphics[width=11.4cm]{figs/RMSD_heatmap/RMSD_heatmap.pdf}
\caption{\label{fig:RMSD_heatmap}
{\bf Sites with strongly shifted amino-acid preferences between H3 and H1 HAs.}
(A) The shift in amino-acid preferences between the H3 and H1 HA at each site as calculated in Figure~\ref{fig:distance_distribution}C is mapped onto the structure of the H3 HA. 
(B) Amino-acid preferences of sites in the stalk domain are less shifted than those in the head domain.
Sites absolutely conserved in all 18 HA subtypes are less shifted than other sites.
Sites with one amino-acid identity in the clade containing H1, H2, H5, and H6 and another identity in the clade containing H3, H4, and H14 are more shifted than other sites.
(C) Sites 107 and 75(HA2) help determine the different orientation of the globular head domain in H1 versus H3 HAs.
These sites are shown in spheres on the structure of H1 and H3. 
One monomer is in dark gray, while the HA1 domain of the neighboring monomer is in lighter gray.
The spheres are colored as in panel (A), and the experimentally measured amino-acid preferences in the WSN/1933 H1 and Perth/2009 H3 HAs are shown.
\comment{Could B be a thinner panel at the bottom, and then C be to the right of A, possibly with H1 and H3 vertically oriented? It may be OK to shrink the A panel a bit if that save space in this new layout.}
}
\end{SCfigure*}

>>>>

%\begin{SCfigure*}[\sidecaptionrelwidth][t]
\begin{figure}
\centering
%\includegraphics[width=11.4cm]{figs/RMSD_heatmap/RMSD_heatmap.pdf}
\includegraphics[width=\columnwidth]{figs/RMSD_heatmap/RMSD_heatmap.pdf}
\caption{\label{fig:RMSD_heatmap}
{\bf Sites with strongly shifted amino-acid preferences between H3 and H1 HAs.}
(A) The shift in amino-acid preferences between the H3 and H1 HA at each site as calculated in Figure~\ref{fig:distance_distribution}C is mapped onto the structure of the H3 HA. 
(B) Amino-acid preferences of sites in the stalk domain are less shifted than those in the head domain.
Sites absolutely conserved in all 18 HA subtypes are less shifted than other sites.
Sites with one amino-acid identity in the clade containing H1, H2, H5, and H6 and another identity in the clade containing H3, H4, and H14 are more shifted than other sites.
(C) Sites 107 and 75(HA2) help determine the different orientation of the globular head domain in H1 versus H3 HAs.
These sites are shown in spheres on the structure of H1 and H3. 
One monomer is in dark gray, while the HA1 domain of the neighboring monomer is in lighter gray.
The spheres are colored as in panel (A), and the experimentally measured amino-acid preferences in the WSN/1933 H1 and Perth/2009 H3 HAs are shown.
}
%\end{SCfigure*}
\end{figure}
